A Reproducible Data Analysis Workflow with RMarkdown, Git, Make & Docker

### 2019-10-29 rr-flow.Rmd
make link clickable

This paper is fully reproducible using the workflow described in this paper. All materials, including the manuscript source and all R codes and files used to generate this manuscript, can be found on the accompanying GitHub repository <https://GitHub.com/aaronpeikert/reproducible-research/>.

>>>>

This paper is fully reproducible using the workflow described in this paper. All materials, including the manuscript source and all R codes and files used to generate this manuscript, can be found on the accompanying GitHub repository [<https://github.com/aaronpeikert/reproducible-research/>](https://github.com/aaronpeikert/reproducible-research/).
